Inference methods comparison for the simplified Naomi model

### 2023-02-21 src/naomi-simple_compare/comparison.Rmd
Fix jitter height issue, add gradient to scatterplots, fix ...Names issue

@@

```{r}
ks_helper("beta", sw = TRUE)
ks_helper("beta", sw = TRUE, method1 = "TMB", method2 = "TMB")
```

@@

  densityplot <- ggplot(ks_summary, aes(x = .data[[ks_method1]], y = .data[[ks_method2]])) +
    stat_density_2d(aes(linetype = Type), col = "black") +
    annotate(geom = "polygon", x = c(-Inf, Inf, Inf), y = c(-Inf, Inf, -Inf), fill = multi.utils::cbpalette()[2], alpha = 0.2) +
    annotate(geom = "polygon", x = c(-Inf, Inf, -Inf), y = c(-Inf, Inf, Inf), fill = multi.utils::cbpalette()[6], alpha = 0.2) +
    xlim(0, 0.75) +
    ylim(0, 0.75) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed", alpha = 0.5) +
    scale_linetype_manual(values = c("dashed", "solid")) +
    # scale_alpha_discrete(range = c(0.5, 0.01)) +
    # guides(alpha = FALSE) +
    guides(linetype = FALSE) +
    labs(x = ks_method1, y = ks_method2) +
    theme_minimal()

@@

  ridgeplot <- ggplot(ks_summary, aes(y = Type, x = `KS difference`)) +
    ggridges::geom_density_ridges(alpha = 0.7, fill = NA, aes(linetype = Type)) +
    coord_flip() +
    scale_linetype_manual(values = c("dashed", "solid")) +
    labs(y = "", x = paste0(ks_method1, " - ", ks_method2)) +
    guides(linetype = FALSE) +
    theme_minimal()

@@

(ks_summary_out <- ks_summary %>%
  group_by(Type) %>%
  summarise(
    TMB = mean(`KS(TMB, tmbstan)`),
    aghq = mean(`KS(aghq, tmbstan)`),
    adam = mean(`KS(adam, tmbstan)`)
  ))
```

>>>>

The `beta_rho` parameter is used in other reports as a check, so create the dataframe to save as artefact here:

@@

```{r}
ks_helper("beta", sw = TRUE)
ks_helper("beta", sw = TRUE, method1 = "TMB", method2 = "adam")
```

@@

  xy_length <- min(1, max(ks_summary[[ks_method1]], ks_summary[[ks_method2]]) + 0.05)

  x <- y <- seq(0, xy_length, length.out = 20)

  gradient_base <- expand.grid(x, y) %>%
    mutate(diff = Var1 - Var2) %>%
    ggplot(aes(x = Var1, y = Var2)) +
    geom_tile(aes(fill = diff), alpha = 0.7) +
    scale_fill_gradientn(
      colours = c("#56B4E9", "white", "#009E73"),
      rescaler = ~ scales::rescale_mid(.x, mid = 0)
    )

  densityplot <- gradient_base +
    stat_density_2d(data = ks_summary, aes(x = .data[[ks_method1]], y = .data[[ks_method2]], linetype = Type), col = "black") +
    xlim(0, xy_length) +
    ylim(0, xy_length) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed", alpha = 0.5) +
    scale_linetype_manual(values = c("solid", "dashed")) +
    labs(x = ks_method1, y = ks_method2) +
    theme_minimal() +
    guides(fill = "none") +
    theme(
      legend.position = "bottom"
    )

@@

  ridgeplot <- ggplot(ks_summary, aes(y = Type, x = `KS difference`)) +
    ggridges::geom_density_ridges(alpha = 0.7, fill = NA, aes(linetype = Type)) +
    coord_flip() +
    scale_linetype_manual(values = c("solid", "dashed")) +
    labs(y = "", x = paste0(ks_method1, " - ", ks_method2)) +
    guides(linetype = FALSE) +
    theme_minimal()

@@

(ks_summary_out <- ks_summary %>%
  group_by(Type) %>%
  summarise(
    TMB = mean(`KS(TMB, tmbstan)`),
    aghq = mean(`KS(aghq, tmbstan)`),
    adam = mean(`KS(adam, tmbstan)`)
  ))
```
Compute $p$-values, then plot expecting $\mathcal{U}(0, 1)$.
If not conclude there is a significant difference.
